Implementing Real-time Transport Services over an Ossified Network

### 2016-05-10 paper.tex
Update pdfinfo

%==================================================================================================
% The following information gets written into the PDF file information:
\pdfinfo{
  /Title        (...)
  /Author       (...)
  /Subject      (...)
  /Keywords     (..., ..., ...)
  /CreationDate (D:20150827110616+01'00')
  /ModDate      (D:20150827110616+01'00')
  /Creator      (LaTeX)
  /Producer     (pdfTeX)
}
%==================================================================================================
\begin{document}
\title{Implementing Real-time Transport Services over an Ossified Network}
\numberofauthors{3}
\author{
  \alignauthor
    Stephen McQuistin\\
    \affaddr{University of Glasgow, UK}\\
    \email{sm@smcquistin.uk}
  \alignauthor
    Colin Perkins\\
    \affaddr{University of Glasgow, UK}\\
    \email{csp@csperkins.org}
  \alignauthor
    Marwan Fayed\\
    \affaddr{University of Stirling, UK}\\
    \email{mmf@cs.stir.ac.uk}
}

>>>>

%==================================================================================================
% The following information gets written into the PDF file information:
\pdfinfo{
  /Title        (Implementing Real-time Transport Services over an Ossified Network)
  /Author       (Stephen McQuistin, Colin Perkins, and Marwan Fayed)
  /Subject      (Real-time Transport Protocols)
  /Keywords     (Transport Services, TCP, TCP Hollywood)
  /CreationDate (D:20160516000000+01'00')
  /ModDate      (D:20160516000000+01'00')
  /Creator      (LaTeX)
  /Producer     (pdfTeX)
}
%==================================================================================================
\begin{document}
\title{Implementing Real-time Transport Services over an Ossified Network}
\numberofauthors{3}
\author{
  \alignauthor
    Stephen McQuistin\\
    \affaddr{University of Glasgow, UK}\\
    \email{sm@smcquistin.uk}
  \alignauthor
    Colin Perkins\\
    \affaddr{University of Glasgow, UK}\\
    \email{csp@csperkins.org}
  \alignauthor
    Marwan Fayed\\
    \affaddr{University of Stirling, UK}\\
    \email{mmf@cs.stir.ac.uk}
}
